\thetitle

### 2022-03-30 paper/paper.tex
benchmark

\ifen
We interpret this problem as the \emph{optimal college application} problem, as follows. Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. (Alternatively, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.) Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. (The problem is also conformable to other competitive matching games such as job application.)
\else
다음 해석에 따라 이를 `대학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. (예산 제약 조건은 또한 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수도 있다.) 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최대값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다. (취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위에 문제를 적용할 수 있다.)
\fi

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize students' application strategy.  To the extent that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 비율은 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정되는 만큼, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

\ifen
From a methodological standpoint, as Chao (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Chao는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

@@

\ifen \subsection{Experimental procedure} \else \subsection{실험 방법}\fi
\def\nmarkets{20}
\ifen
The experimental procedure was as follows. First, to generate synthetic markets, we drew the $t_j$-values independently from an exponential distribution with a scale parameter of ten and rounded up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10\,Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In the first experiment, which concerns Alma's problem, we set each $g_j = 1$ and $H = h = \lfloor m/ 2 \rfloor$. In the second experiment, which concerns Ellis's problem, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we set $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. A typical instance is shown in Figure \ref{samplemarket}.
\else
실험 방법은 다음과 같다. 먼저, 가산 시장을 생성하기 위해 $t_j$-값을 평균이 10인 지수 분포에서 동립적으로 관측하고 정수로 올림했다. 그다음에, $t_j$와 $f_j$가 서로 부분적으로 반비례하게 만들도록 $f_j = 1 / (t_j + 10\,Q)$로 정의했다. 단, $Q$는 $[0, 1)$에서 균일한 확률로 관측한다. 알마의 문제를 고려하는 첫번째 실험에서, 모든 $g_j = 1$ 그리고 $H = h = \lfloor m/ 2 \rfloor$으로 처리했다. 엘리스의 문제를 고려하는 두번째 실험에서, 모든  $g_j$를 $\{5, \dots, 10\}$에서 균일한 확률로 관측했으며 $H = \lfloor \frac{1}{2} \sum g_j \rfloor$으로 처리했다. 그림 \ref{samplemarket}에서 전형적인 인스턴스가 나타난다.
\fi

\ifen
The experimental variables were the market size $m$, the choice of algorithm, and (for Algorithm \ref{ellisDP3}) the tolerance $\varepsilon$. For each combination of the experimental variables, we generated \nmarkets~markets, and the optimal portfolio was computed three times, with the fastest of the three repetitions recorded as the computation time. We then report the mean and standard deviation across the \nmarkets~markets. Therefore, each cell of each table below represents a statistic over {\the\numexpr 3 * \nmarkets \relax}~computations. Where applicable, we did not count the time required to sort the entries of $t$.
\else
실험 변수로는 시장의 크기 $m$, 해법 선택, 그리고 (알고리즘 \ref{ellisDP3}인 경우) 허용치 $\varepsilon$을 고려했다. 실험 변수의 각 조합에 대해,  \nmarkets 개의 시장을 생성했으며 최적 포트폴리오를 3번 계산 한 것 중 가장 빠른 것으로 계산 시간으로 기록했다. \nmarkets 개의 시장에 대한 평균과 평균편차를 표에 나타낸다. 따라서 아래 표의 각 칸은 {\the\numexpr 3 * \nmarkets \relax}개의 계한에 대한 통계다. $t$를 배열하는 시간은 고려하지 않았다.
\fi

@@

\ifen
In the second experiment, we turn to the general problem, and compare the performance of the exact algorithms (Algorithms \ref{ellisbnb} and \ref{ellisDP1}) and the approximation scheme (Algorithm \ref{ellisDP3}) at tolerances 0.5 and 0.05.  The results, which appear in Table \ref{experiment2results}, broadly agree with the time complexity analyses presented above. Overall, we found the exact dynamic program to be the fastest algorithm, while the FPTAS was rather slow, a result that echoes the results of computational studies on knapsack problems (Martello and Toth 1990, \S\,2.10). The branch-and-bound algorithm proved impractical for even medium-sized instances. 
\else
두번째 실험에서 일반적 문제를 고려한다. 정확한 해법 (알고리즘 \ref{ellisbnb} 및 알고리즘 \ref{ellisDP1}) 그리고 허용치를 0.5와 0.05로 설정한 근사 해법 (알고리즘 \ref{ellisDP3})의 성능을 비교한다. 실험 결과는 표 \ref{experiment1results}에서 나타나며 위에서 도출한 시간 복잡성 결과와 대략 같다. 정확한 동적계획 해법이 전책적으로 가장 빠르며 FPTAS가 약간 느린 것으로 나온 결과는 배낭 문제 해법을 비교한 기존 연구와 비슷하다 (Martello와 Toth 1990, \S\,2.10). 분지한계법은 크기가 중간인 인스턴스에 대해서도 비효율적이었다. 
\fi

\newcommand{\missing}{---}
\newcommand{\lastptofcaption}{\ifen
For each value of $m$, \nmarkets~markets were generated, and the computation time was recorded as fastest of three repetitions of the algorithm. The table shows the average time (standard deviation) over the \nmarkets~instances.
\else 각 $m$에 대해 \nmarkets 개의 시장을 생성했으며 알고리즘을 3번 반복해서 그 중 최소 계산 시간을 기록했다. 표에서 \nmarkets 개의 인스턴스에 대한 평균 (평균편차) 시간이 나타난다.\fi}

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &     0.00 &  (0.00) &      0.01 &    (0.00) \\
    64 &     0.01 &  (0.00) &      0.13 &    (0.03) \\
   256 &     0.14 &  (0.02) &      1.56 &    (0.57) \\
  1024 &     2.21 &  (0.35) &     41.65 &   (10.55) \\
  4096 &    35.36 &  (4.96) &   5080.63 & (6266.66) \\
 16384 &   552.45 & (79.57) &  16452.20 & (5525.29)       
\end{tabular}
\caption{\label{experiment1results} \normalsize
\ifen Time in ms to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as a list and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 목록 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. 단위: ms. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}

>>>>

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. (Alternatively, the budget constraint may represent the time needed to complete each application, or a legal limit on the number of applications permitted.) Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. (The problem is also conformable to other competitive matching games such as job application.)
\else
다음 해석에 따라 이를 `대학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. (예산 제약 조건은 또한 원서를 작성하는 시간이나 지원 개수에 대한 법적인 제한을 나타낼 수도 있다.) 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최대값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다. (취직 전략과 같은 유사한 경쟁적 매칭 게임에도 위에 문제를 적용할 수 있다.)
\fi

\ifen
The college application problem is not solely of theoretical interest. In the American college consulting industry, students pay private consultants an average of \$200 per hour for assistance in preparing application materials, estimating their admissions odds, and identifying target schools (Sklarow 2018). In Korea, an important revenue stream for admissions consulting firms such as Megastudy (\url{megastudy.net}) and Jinhak (\url{jinhak.com}) is ``mock application'' software that claims to use artificial intelligence to optimize the client's application strategy.  Due to the widespread perception that career earnings depend on college admissions outcomes, the solution of \eqref{headlineproblem} holds monetary value. However, although predicting admissions outcomes on a school-by-school basis is a standard benchmark for regression models (Acharya et al. 2019), we believe our study is the first to formulate the overall application strategy as an optimization problem. 
\else
대학 지원 최적화 문제는 이론적인 화제일 뿐만이 아니다. 미국 입학 컨설팅 산업에서 대학 지원 서류 작성, 합격 확률 추정, 그리고 지원 학교를 선택하는 데에 자문하는 개인 상담가의 시간당 비율은 평균 200달러이다 (Sklarow 2018). 한국에서, 메가스터디(\url{megastudy.net})와 진학(\url{jinhak.com})과 같은 입학 컨설팅 기업의 주된 수입원 중 인공지능을 활용해서 학생의 지원 전략을 최대화한다고 홍보하는 ``모의 지원'' 소프트웨어가 있다. 미래의 소득이 대학 입학 결과로 결정된다는 넓은 인식에 따라, \eqref{headlineproblem}의 최적해는 금전적인 가치를 가지고 있다. 그러나, 학교 개별 합격 확률을 추정하는 것은 회귀 분석 모형의 익숙한 응용 사례(Acharya et al. 2019)이지만, 전체적인 지원 전략을 최적화 문제로 모형화한 것은 본 연구의 새로운 기여로 보인다.
\fi

\ifen
From a methodological standpoint, as Chao (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her equilibrium model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Chao는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 균형 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

@@

\ifen \subsection{Experimental procedure} \else \subsection{실험 방법}\fi
\def\nmarkets{50}
\ifen
The experimental procedure was as follows. First, to generate synthetic markets, we drew the $t_j$-values independently from an exponential distribution with a scale parameter of ten and rounded up to the nearest integer. To achieve partial negative correlation between $t_j$ and $f_j$, we then set $f_j = 1 / (t_j + 10\,Q)$, where $Q$ is drawn uniformly from the interval $[0, 1)$. In the first experiment, which concerns Alma's problem, we set each $g_j = 1$ and $H = h = \lfloor m/ 2 \rfloor$. In the second experiment, which concerns Ellis's problem, each $g_j$ is drawn uniformly from the set $\{5, \dots, 10\}$ and we set $H = \lfloor \frac{1}{2} \sum g_j \rfloor$. This cost distribution resembles real-world college application fees, which are often multiples of \$10 between \$50 and \$100. A typical instance is shown in Figure \ref{samplemarket}.
\else
실험 방법은 다음과 같다. 먼저, 가산 시장을 생성하기 위해 $t_j$-값을 평균이 10인 지수 분포에서 동립적으로 관측하고 정수로 올림했다. 그다음에, $t_j$와 $f_j$가 서로 부분적으로 반비례하게 만들도록 $f_j = 1 / (t_j + 10\,Q)$로 정의했다. 단, $Q$는 $[0, 1)$에서 균일한 확률로 관측한다. 알마의 문제를 고려하는 첫번째 실험에서, 모든 $g_j = 1$ 그리고 $H = h = \lfloor m/ 2 \rfloor$으로 처리했다. 엘리스의 문제를 고려하는 두번째 실험에서, 모든  $g_j$를 $\{5, \dots, 10\}$에서 균일한 확률로 관측했으며 $H = \lfloor \frac{1}{2} \sum g_j \rfloor$으로 처리했다. 실제 대학 지원 비용인 50~100달러 사이에 10달러의 어떤 배수이므로 합리적인 비용 분포이다. 그림 \ref{samplemarket}에서 전형적인 인스턴스가 나타난다.
\fi

\ifen
The experimental variables were the market size $m$, the choice of algorithm, and (for Algorithm \ref{ellisDP3}) the tolerance $\varepsilon$. For each combination of the experimental variables, we generated \nmarkets~markets, and the optimal portfolio was computed three times, with the fastest of the three repetitions recorded as the computation time. We then report the mean and standard deviation across the \nmarkets~markets. Therefore, each cell of each table below represents a statistic over {\the\numexpr 3 * \nmarkets \relax}~computations. Where applicable, we do not count the time required to sort the entries of $t$.
\else
실험 변수로는 시장의 크기 $m$, 해법 선택, 그리고 (알고리즘 \ref{ellisDP3}인 경우) 허용치 $\varepsilon$을 고려했다. 실험 변수의 각 조합에 대해,  \nmarkets 개의 시장을 생성했으며 최적 포트폴리오를 3번 계산 한 것 중 가장 빠른 것으로 계산 시간으로 기록했다. \nmarkets 개의 시장에 대한 평균과 평균편차를 표에 나타낸다. 따라서 아래 표의 각 칸은 {\the\numexpr 3 * \nmarkets \relax}개의 계한에 대한 통계다. $t$를 배열하는 시간은 고려하지 않았다.
\fi

@@

\ifen
In the second experiment, we turn to the general problem, and compare the performance of the exact algorithms (Algorithms \ref{ellisbnb} and \ref{ellisDP1}) and the approximation scheme (Algorithm \ref{ellisDP3}) at tolerances 0.5 and 0.05.  The results, which appear in Table \ref{experiment2results}, broadly agree with the time complexity analyses presented above. The branch-and-bound algorithm proved impractical for even medium-sized instances. Overall, we found the exact dynamic program to be the fastest algorithm, while the FPTAS was rather slow, a result that echoes the results of computational studies on knapsack problems (Martello and Toth 1990, \S\,2.10).

The strong performance of Algorithm \ref{ellisDP1} is partly attributable to the structure of our synthetic instances, in which application costs are small integers and $H$ is proportional in expectation to $m$, meaning the expected computation time is $O(m^2)$. However, the relative advantage of Algorithm \ref{ellisDP1} is even more pronounced in real college-application instances because the typical student's application budget accommodates at most a dozen or so schools and is constant in $m$. 
\else
두번째 실험에서 일반적 문제를 고려한다. 정확한 해법 (알고리즘 \ref{ellisbnb} 및 알고리즘 \ref{ellisDP1}) 그리고 허용치를 0.5와 0.05로 설정한 근사 해법 (알고리즘 \ref{ellisDP3})의 성능을 비교한다. 실험 결과는 표 \ref{experiment1results}에서 나타나며 위에서 도출한 시간 복잡성 결과와 대략 같다. 정확한 동적계획 해법이 전책적으로 가장 빠르며 FPTAS가 약간 느린 것으로 나온 결과는 배낭 문제 해법을 비교한 기존 연구와 비슷하다 (Martello와 Toth 1990, \S\,2.10). 분지한계법은 크기가 중간인 인스턴스에도 비효율적이었다.

알고리즘 \ref{ellisDP1}의 좋은 실험적 성능은 부분적으로 가상 인스턴스의 구조 덕이다. 가상 인스턴스의 지원 비용이 작은 정수이고 $H$가 $m$과 선형식으로 비례하는 것은 알고리즘의 기대 계산 시간이 $O(m^2)$임을 의미한다. 그러나 전형적인 학생의 지원 예산은 최대한 열 몇 개의 학교에 지원할 수 있게 하며 $m$에 대해 상수이므로, 실제 대학 지원 문제 인스턴스에 적용하면 알고리즘 \ref{ellisDP1}이 더욱 뚜렷한 상대적 우위를 발휘한다. 
\fi

\newcommand{\lastptofcaption}{\ifen
For each value of $m$, \nmarkets~markets were generated, and the computation time was recorded as fastest of three repetitions of the algorithm. The table shows the average time (standard deviation) over the \nmarkets~instances.
\else 각 $m$에 대해 \nmarkets 개의 시장을 생성했으며 알고리즘을 3번 반복해서 그 중 최소 계산 시간을 기록했다. 표에서 \nmarkets 개의 인스턴스에 대한 평균 (평균편차) 시간이 나타난다.\fi}

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r}
\ifen 
 \textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with list\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{algorithmforlargeh}\\with heap\end{tabular}}}\\ \hline
 \else
 \textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}& \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(목록 구현)\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{algorithmforlargeh}\\(힙 구현)\end{tabular}}}\\ \hline
 \fi
    16 &           0.00 &        (0.00) &           0.02 &        (0.01) \\
    64 &           0.03 &        (0.00) &           0.17 &        (0.05) \\
   256 &           0.14 &        (0.03) &           2.20 &        (0.73) \\
  1024 &           2.08 &        (0.65) &          30.51 &        (6.37) \\
  4096 &          28.87 &       (10.60) &         485.80 &       (90.50) \\
 16384 &         369.79 &      (127.38) &        9780.83 &     (1888.34)  
\end{tabular}
\caption{\label{experiment1results} \normalsize
\ifen Time in ms to compute an optimal portfolio for an admissions market with homogeneous application costs using Algorithm \ref{algorithmforlargeh} when $\mathcal{C}$ is stored as a list and as a heap. \lastptofcaption~In every case, $h = m/2$. 
\else 알고리즘 \ref{algorithmforlargeh}에서 $\mathcal{C}$를 목록 또는 힙 구현으로 저장했을 때, 
동일 지원 비용 입학 시장의 최적 지원 포트폴리오를 계산하는 시간. 단위: ms. \lastptofcaption~모든 경우, $h = m/2$. \fi}
\end{table}

\begin{table}[h!] \centering
\small
\begin{tabular}{r|r@{~}r|r@{~}r|r@{~}r|r@{~}r}
\ifen
\textbf{\begin{tabular}[r]{@{}r@{}}Number of\\schools $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisbnb}:\\Branch \& bound\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP1}:\\App. costs DP\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Algorithm \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\else
\textbf{\begin{tabular}[r]{@{}r@{}}학교의\\개수 $m$\end{tabular}}&\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘  \ref{ellisbnb}:\\분지한계법\end{tabular}}}  & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP1}: 지원\\비용 동적 계획\end{tabular}}}  &\multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.5$\end{tabular}}}  & \multicolumn{2}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}알고리즘 \ref{ellisDP3}:\\FPTAS, $\varepsilon= 0.05$\end{tabular}}}   \\ \hline
\fi
    8 &          0.05 &       (0.03) &         0.02 &      (0.01) &                0.08 &             (0.02) &                 0.28 &              (0.09) \\
   16 &          0.37 &       (0.25) &         0.10 &      (0.03) &                0.53 &             (0.15) &                 4.39 &              (1.27) \\
   32 &        131.58 &     (172.60) &         0.40 &      (0.10) &                3.08 &             (0.70) &                45.07 &             (15.72) \\
   64 &             — &          (—) &         1.78 &      (0.46) &               20.91 &             (4.81) &               566.75 &            (149.18) \\
  128 &             — &          (—) &         9.34 &      (1.98) &              121.28 &            (33.50) &              3090.48 &            (863.95) 
\end{tabular}%
\caption{\label{experiment2results} \normalsize
\ifen Time in ms to compute an optimal or $(1 - \varepsilon)$-optimal portfolio for an admissions market with heterogeneous application costs using the three algorithms developed in section \ref{hetappcosts}.
%branch-and-bound routine (Algorithm \ref{ellisbnb}), exact dynamic program (Algorithm \ref{ellisDP1}), and the fully polynomial-time approximation scheme (Algorithm \ref{ellisDP3}).
The branch-and-bound algorithm is impractical for large markets. \lastptofcaption
\else  %분지한계법 (알고리즘 \ref{ellisbnb}), 정확한 동적 계획 (알고리즘 \ref{ellisDP1}), 그리고 완전 다항 시간 근사 해법 (알고리즘 \ref{ellisDP3})을
 \ref{hetappcosts}절에서 도출한 3개의 알고리즘을 사용할 때, 다양한 지원 비용으로 갖춘 입학 시장의 최적 또는 $(1- \varepsilon)$-최적 포트폴리오를 계산하는 시간. 단위: ms. 분지한계법은 큰 시장에서 비실용적이다. \lastptofcaption \fi}
\end{table}
